### 2013-03-22 doc/sosp13/method.tex

@@

\paragraph{Unbalanced tree search in-memory (UTS-Mem)} Unbalanced Tree
Search (UTS) is a benchmark for evaluating the programmability and
performance of systems for parallel applications that require dynamic
load balancing~\cite{UTS}. It involves traversing an
unbalanced implicit tree: at each vertex, its number of children is
sampled from some probability distribution, and this number of new nodes
are added to a work queue to be visited. While this benchmark captures
irregular, dynamic \emph{computation}, we actually want to evaluate
performance of algorithms with irregular \emph{memory} access patterns.
Thus we augment UTS by using the existing traversal code to create a
large tree in memory, and then we traverse the in-memory tree. We call
this benchmark UTS-Mem, and the timed portion is this traversal of the
in-memory tree. This in-memory traversal has no knowledge of the
tree structure beforehand.  The Grappa version of the in-memory tree
search uses the asynchronous parallel for loop over a visited vertex's
children list.

@@

\paragraph{Breadth-first-search (BFS)}
This is the primary kernel for the Graph500 benchmark and is what
currently determines the ranking of machines on the Graph500
list~\cite{graph500list}. As a whole, the Graph500 benchmark suite is
designed to bring the focus of system design on data-intensive
workloads, particularly large-scale graph analysis problems, that are
important among cybersecurity, informatics, and network understanding
workloads. The BFS benchmark builds a search tree containing parent
nodes for each traversed vertex during the search.  While this is a
relatively simple problem to solve, it exercises the random-access and
fine-grained synchronization capabilities of a system as well as being
a primitive in many other graph algorithms. Performance is measured in
\emph{traversed edges per second} (TEPS), where the number of edges is
the edges making up the generated BFS tree. One of the reference
implementations of Graph500 BFS is for the XMT; this code fails to
scale past 16 XMT processors because it does not expose enough
parallelism, so we modified the code to use a recursive loop
decomposition similar to Grappa's. We compare this modified version
against a straightforward Grappa implementation. We do not employ
algorithmic improvements, though there are
many~\cite{Beamer:Graph500,Yoo:FixedPointGraph500}.

>>>>

\TODO{Need to rewrite once our evaluations story is solid. We need to talk about MPI and why that comparison makes sense.}

@@

\paragraph{Unbalanced tree search in-memory (UTS-Mem)} Unbalanced Tree
Search (UTS) is a benchmark for evaluating the programmability and
performance of systems for parallel applications that require dynamic
load balancing~\cite{UTS}. It involves traversing an
unbalanced implicit tree: at each vertex, its number of children is
sampled from some probability distribution, and this number of new nodes
are added to a work queue to be visited. While this benchmark captures
irregular, dynamic \emph{computation,} we actually want to evaluate
performance of algorithms with irregular \emph{memory\/} access patterns.
Thus we augment UTS by using the existing traversal code to create a
large tree in memory, and then we traverse the in-memory tree. We call
this benchmark UTS-Mem, and the timed portion is this traversal of the
in-memory tree. This in-memory traversal has no knowledge of the
tree structure beforehand.  The Grappa version of the in-memory tree
search uses the asynchronous parallel for loop over a visited vertex's
children list.

@@

\paragraph{Breadth-first-search (BFS)}
This is the primary kernel for the Graph500 benchmark and is what
currently determines the ranking of machines on the Graph500
list~\cite{graph500list}. As a whole, the Graph500 benchmark suite is
designed to bring the focus of system design on data-intensive
workloads, particularly large-scale graph analysis problems, that are
important among cybersecurity, informatics, and network understanding
workloads. The BFS benchmark builds a search tree containing parent
nodes for each traversed vertex during the search.  While this is a
relatively simple problem to solve, it exercises the random-access and
fine-grained synchronization capabilities of a system as well as being
a primitive in many other graph algorithms. Performance is measured in
\emph{traversed edges per second\/} (TEPS), where the number of edges is
the edges making up the generated BFS tree. One of the reference
implementations of Graph500 BFS is for the XMT; this code fails to
scale past 16 XMT processors because it does not expose enough
parallelism, so we modified the code to use a recursive loop
decomposition similar to Grappa's. We compare this modified version
against a straightforward Grappa implementation. We do not employ
algorithmic improvements, though there are
many~\cite{Beamer:Graph500,Yoo:FixedPointGraph500}.
